Hidden Talents Multiverse Analysis

### 2021-07-02 README.Rmd
add a how to reproduce this repo section to README

@@

>>>>

To reproduce this repository, see [How to reproduce this respository](#repro) below.

@@

## How to reproduce this repository {#repro}

To reproduce this repository, download all files locally. You can do this by cloning the repository or downloading the files directly as a .zip file. Because many of the objects are very large (i.e., those containing multiverse data and results), they are not included in this repository. However, the scripts will create all necessary outputs to reproduce all data and files. Below is the exact order these scripts should be ran:

### 1.  Data Preparation

1. `1-data-prep/1-data-non-arbitrary.R`
2. `1-data-prep/2-primary-multiverse-datasets.R`
3. `1-data-prep/3-sedoncary-multiverse-datasets.R`

### 2.  Primary Analyses

1. `2-primary-analyses/1-confirmatory.R`: conducts unpredictability and violence multiverse analyses for attention-shifting and working memory updating.
2. `2-primary-analyses/1-exploratory.R`: conducts poverty multiverse analyses for attention-shifting and working memory updating.
3. `2-primary-analyses/1-extract-effects.R`: extracts and compiles multiverse data for plotting and reporting.
4. `2-primary-analyses/1-bootstrap-setup.R`: sets up bootstrap samples for bootstrapping technique .
5. `2-primary-analyses/1-bootstrap-spec-analysis.R`: runs specification analyses over all bootstrapped samples to obtain overall *p*-values.

### 3. Secondary Analyses

1. Set 1
    1. `3-secondary-analyses/set-1/a1-analysis-ses-vio.R`: conducts secondary analysis labeled "Comparing Violence and Poverty Exposure Interactions with Task-Version" in the manuscript
    2. `3-secondary-analyses/set-1/a2-extract-effects.R`: extracts and compiles multiverse data for plotting and reporting for the analysis labeld "Comparing Violence and Poverty Exposure Interactions with Task-Version" in the manuscript.
    3. `3-secondary-analyses/set-1/b1-analysis-ses-components.R`: conducts an analysis of the components of poverty, which is redundant with the secondary analysis labeled "Exploring Components of Adversity Dimensions", which is conducted below in Set 2. 
    4. `3-secondary-analyses/set-1/b2-extract-effects.R`: extracts effects for poverty component multiverse analyses.
2. Set 2
    1. `3-secondary-analyses/set-2/a1-analysis-adversity-components.R`: conducts an analysis of the components of all adversity composites for the secondary analysis labeled "Exploring Components of Adversity Dimensions" (this is an expansion of the above secondary analysis for the components of poverty in Set 1) 
    2. `3-secondary-analyses/set-2/a2-extract-effects.R`: extracts effects for adversity component multiverse analyses.

### 4. Manuscript

1. `manuscript/scripts/rmd-staging.R`: loads all necessary data and multiverse objects, computes all necessary in-text statistics, and sources the following scripts to create tables and figures for the manuscript stored in `manuscirpt/staged-objects.Rdata`:
    - `table1.R`
    - `table2.R`
    - `table3.R`
    - `figure2-3.R`
2. `manuscript/manuscript.Rmd`: loads `manuscript/staged-objects.Rdata` and knits together the written manuscript and all statistics, tables, and figures computed by the staging script above.

### 5. Supplement

1. `supplement/scripts/rmd-staging.R`: loads all necessary data and multiverse objects and sources the following scripts to create tables and figures for the supplement stored in `supplement/staged-objects.Rdata`:
    - `1-covariates.R`
    - `2-secondary1.R`
    - `3-secondary2.R`
    - `4-tables.R`
2. `supplement/supplement.Rmd`: loads `supplement/staged-objects.Rdata` and knits together the written supplement and all tables and figures computed by the staging script above.
